# Exploratory Data Analysis {#dataanalysis}


```{r, include=FALSE}
#Loading Packages 
library(magrittr)
library(tidyverse)
library(dplyr)
library(naniar)
library(kableExtra)
library(mice)
library(skimr)
```

```{r}
#note; In real world analysis, EDA will be done before handling missing values
#Import Data with Missing Values

data<-read.csv("data/CleanedData.csv",header = T,colClasses=c("NULL", rep(NA, 13))) 
```



```{r}
library(ggplot2)

hepatitis = subset(data, Category==1)
healthyBlood = subset(data, Category==0)

 ggplot() + geom_density(aes(x=AST), colour="red", data=hepatitis) +
  geom_density(aes(x=AST), colour="Green", data=healthyBlood) +
  ggtitle(" Density Plot of Category VS. AST") +
  theme(plot.title = element_text(hjust = 0.5))

```

**COMMENT**
From the aBove plot,we can see that,density of AST of healthy blood donors and hepatitis C pateient are positive skewed.


## FINDINGS

```{r}

par(mfrow=c(1,2))
hist(hepatitis$AST, col="green", xlab = "AST", main = "Histogram of AST OF Hepatistics C Patient")
hist(healthyBlood$AST, col="green", xlab = "AST", main = "Histogram of AST of healthy blood patient")


hist(hepatitis$GGT, col="red", xlab = "GGT", main = "Histogram of GGT Hepatistics C Patient")
hist(healthyBlood$GGT, col="red", xlab = "GGT", main = "Histogram of GGT healthy blood patient")

hist(hepatitis$BIL, col="blue", xlab = "BIL", main = "Histogram of BIL Hepatistics C Patient")
hist(healthyBlood$BIL, col="blue", xlab = "BIL", main = "Histogram of BIL healthy blood patient")
```


we can observe that,with the AST variable,the data is skewed to the hepatitis C patient with lesser values to the Healh blood patients.This observation can also be observe from GGT.

We can observe from the 3rd plot that,the largerobservations correspond to the healthy blood donors unlike the first two plots.




<!-- ## OUTLIER DETECTION -->

<!-- ```{r} -->
<!-- #Outlier detection -->


<!-- library(isofor) -->
<!-- hep<-data[data$Category==1,]                          #Data for Hepatitis C patient -->
<!-- healt.bd<-data[data$Category==0,]                     #Data for Healthy blood donors -->

<!-- fit.isoforest <- iForest(hep[,-c(1,3)], nt=100, phi=256) -->
<!-- pred <- predict(fit.isoforest, newdata=healt.bd[,-c(1,3)]) -->

<!-- ``` -->


<!-- ```{r} -->



<!-- # PLOT OF THE SCORES -->
<!-- score <- scale(pred, center = min(pred), scale = max(pred)-min(pred)) -->
<!-- par(mfrow=c(1,1), mar=rep(4,4)) -->
<!-- plot(x=1:length(score), score, type="p", pch=19, main="Anomaly Score via iForest",xlab="id", ylab="score", cex=score*3, col="coral2") -->
<!-- add.seg <- function(x) segments(x0=x[1], y0=0, x1=x[1], y1=x[2], lty=1, lwd=1.5, col="cadetblue") -->
<!-- apply(data.frame(id=1:length(score), score=score), 1, FUN=add.seg) -->
<!-- eps <- 0.99 -->
<!-- id.outliers <- which(score > quantile(score, eps)) -->
<!-- text(id.outliers, score[id.outliers]+0.03, label=id.outliers,  -->
<!--      col="deepskyblue2", cex=0.7)  -->
<!-- id.outliers -->
<!-- ``` -->


<!-- **COMMENT** -->

<!-- The isoForest is used for anomaly detection.I discarded the categorical/dummy predictors since they can't be outlliers.The model is fitted with the trained healthy blood donors and predictions was made on the Hepatis C data.We observe from the plot that,this method efficiently predictedthe outliers in the Hpatitis C data.The ID's considered as outliers are 206 534 537 538 539 540 -->
